Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-06 paper.tex
Small changes

@@

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to some learning algorithm, some estimators in the library implement
a \textit{transformer} interface which defines a \texttt{transform} method
taking as input some dataset \texttt{X} and yielding as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

@@

A distinguishing feature of scikit-learn estimators
is that they can be composed into \texttt{Pipeline} objects.
Such objects combine typical machine learning workflows
(extracting features, centering/scaling/normalization,
feature selection, making predictions)
in a single object that is itself an estimator,
and whose methods cause data to flow through the pipeline.
More importantly, though, they can be used for
systematic, automated model selection.
This is best explained by example.

>>>>

\textcolor{red}{TODO: focus on the experience we accumulated (general remark).}

@@

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to a learning algorithm, some estimators in the library implement a
\textit{transformer} interface which defines a \texttt{transform} method. It
takes as input some dataset \texttt{X} and yields as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

@@

A distinguishing feature of the \textit{scikit-learn} API is its ability to
compose new estimators from several base estimators. Composition mechanisms can
be used to combine typical machine learning workflows (e.g., feature extraction,
centering/scaling/normalization, feature selection, learning) into a single
object which is itself an estimator. Relying on duck typing, composed estimators
can be used wherever usual estimators can be used. In particular, they integrate
within model selection routines, allowing one to optimize at once every step of
a complex workflow. Composition of estimators can be done in two ways: either
sequentially through \texttt{Pipeline} objects or in a parallel fashion through
\texttt{FeatureUnion} objects.

\vspace{3cm}

A distinguishing feature of \textit{scikit-learn} estimators
is that they can be composed into \texttt{Pipeline} objects.
Such objects combine typical machine learning workflows
(extracting features, centering/scaling/normalization,
feature selection, making predictions)
in a single object that is itself an estimator,
and whose methods cause data to flow through the pipeline.
More importantly, though, they can be used for
systematic, automated model selection.
This is best explained by example.
